\subsection{Introduction}

\begin{frame}[t]{Examples}
\begin{itemize}
  \item You can get all the examples at:
\end{itemize}
\vspace{1cm}
\large
\textbf{\url{https://github.com/jdgarciauc3m/gtesttalk}}
\end{frame}

\begin{frame}[t]{What is Google Test?}
\begin{itemize}
  \item A library to perform unit testing in C++.
  
  \vfill
  \item \textenum{Features}:
    \begin{itemize}
      \item A \textmark{xUnit}-like framework.
      \item Test discovery.
      \item Variety on assertions.
      \item User defined assertions.
      \item \emph{Death tests}.
      \item Fatal and non-fatal failures.
      \item Value parametrized tests.
      \item Type parametrized tests.
      \item Multiple execution options.
      \item XML reporting.
    \end{itemize}

\end{itemize}
\end{frame}

\begin{frame}[t]{Use}
\begin{itemize}
  \item \textenum{Platforms}:
    \begin{itemize}
      \item Linux
      \item Mac OS X
      \item Windows
      \item Cygwin
      \item MinGW
      \item Windows Mobile
      \item Symbian
    \end{itemize}
  \vfill
  \item Some projects \textenum{using} it:
    \begin{itemize}
      \item \textmark{Chromium} Project.
      \item \textmark{LLVM} compiler family.
      \item \textmark{Protocol Buffers}.
      \item \textmark{OpenCV}.
    \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}[t]{Principles}
\begin{enumerate}
  \item Tests should be \textmark{independent} and \textmark{repeatible}.
  \item Tests should be \textmark{well structured}.
  \item Tests should be \textmark{portable} y \textmark{reusable}.
  \item On failure, tests should give \textmark{maximum information}.
  \item Tests should not require writing \textmark{boilerplate code} for
        carrying out tests.
  \item Testing should be \textmark{fast}.
\end{enumerate}
\end{frame}

\begin{frame}[t,fragile]{How do I get Google Test?}
\begin{itemize}
  \item Repo in GitHub.
    \begin{itemize}
      \item \url{https://github.com/google/googletest}
    \end{itemize}
  \vfill
  \item You can get as a pakcage (Ubuntu/Linux).
    \begin{itemize}
      \item Package: \cppid{libgtest-dev}.
      \item \textbad{Important}: Does not intall binaries, only source code.
    \end{itemize}
\end{itemize}
\begin{lstlisting}[style=terminal]
$ apt-get install libgtest-dev
$ cd /usr/src/gtest
$ sudo mkdir build
$ cd build
$ sudo cmake ..
$ sudo make
$ sudo cp *.a /usr/lib
\end{lstlisting}
\end{frame}
